`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-17 inst/manuscript/manuscript.rmd
Fix erroneous citation doublication;

To interrogate factors of this functional class, we have developed a biochemical 
assay suited to characterize scramblase activity in purified proteins and protein 
extracts [@chang_chemical_2004] based on the reconstitution of scramblases or 
candidate proteins into synthetic liposomes with a lipid
composition that includes nitrobenzoxadiazole (NBD) labeled fluorescent lipids.
Upon exposure of these liposomes to membrane-impermeable reducing agents such as 
dithionite, fluorophores in the external leaflet are quenched and fluorescence in scramblase-free liposomes accordingly quickly drops to approximately 50% of the 
initial value. However, for proteoliposomes reconstituted with proteins 
conferring a scramblase activity, fluorescence disappears entirely, as
fast scramblase-mediated equilibration between outer (exposed) and inner
(protected) leaflet of the bilayer renders all fluorescent lipids
accessible to reduction. By titration of the protein amount reconstituted into
the liposome membranes it is thus possible to characterize scramblases and probe
their activity. Beyond the identification of scramblase activities in crude 
membrane preparations [@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
functional validation of candidate scramblases [@menon_opsin_2011;@goren_constitutive_2014;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014], the assay has also been used to characterize the stoichiometry of scramblase homo-multimers reconstituting into the proteoliposomes 
[@ploier_perturbed_submitted] and probe the ATP-dependence of flippases, 
molecules that under energy-consumption flip lipids against a concentration 
gradient between bilayer leaflets [@soupene_atp8a1_2008].
**Are you aware of further use? More adoption would fortify the need for the 
package ...**

>>>>

To interrogate factors of this functional class, we have developed a biochemical 
assay suited to characterize scramblase activity in purified proteins and protein 
extracts [@chang_chemical_2004] based on the reconstitution of scramblases or 
candidate proteins into synthetic liposomes with a lipid
composition that includes nitrobenzoxadiazole (NBD) labeled fluorescent lipids.
Upon exposure of these liposomes to membrane-impermeable reducing agents such as 
dithionite, fluorophores in the external leaflet are quenched and fluorescence in scramblase-free liposomes accordingly quickly drops to approximately 50% of the 
initial value. However, for proteoliposomes reconstituted with proteins 
conferring a scramblase activity, fluorescence disappears entirely, as
fast scramblase-mediated equilibration between outer (exposed) and inner
(protected) leaflet of the bilayer renders all fluorescent lipids
accessible to reduction. By titration of the protein amount reconstituted into
the liposome membranes it is thus possible to characterize scramblases and probe
their activity. Beyond the identification of scramblase activities in crude 
membrane preparations [@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
functional validation of candidate scramblases [@menon_opsin_2011;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014], the 
assay has also been used to characterize the stoichiometry of scramblase 
homo-multimers reconstituting into the proteoliposomes 
[@ploier_perturbed_submitted] and probe the ATP-dependence of flippases, 
molecules that under energy-consumption flip lipids against a concentration 
gradient between bilayer leaflets [@soupene_atp8a1_2008].
**Are you aware of further use? More adoption would fortify the need for the 
package ...**
